Iroko: Predictive Datacenter Congestion Control

### 2017-12-11 Documents/Report/eval.tex
Evaluation: second draft

\begin{figure*} 
	\centering 
	\includegraphics[width=1\linewidth]{rate.png} 
	\caption{}
	\label{fig:rate} 
\end{figure*}

In Figure \ref{fig:rate} we show the aggregate bisection bandwidth. Iroko
consistently provides better utilization compared to ECMP and DCTCP in almost
all experiments. As expected non-blocking is providing the best performance out
of all four techniques. Utilization of non-blocking is lower for traffic
patterns with high incast. Hedera perform extremely well in all experiments
except for some where Iroko outperforms Hedera. Interestingly enough, Hedera
even outperforms non-blocking limit in stride8 experiment. ECMP does reasonably
well when there is high probability of local communication for example smaller
strides, but start to deteriorate as the stride length increases because of hash
collisions.

Another interesting observation is that DCTCP gives abysmal utilization for some
experiments. Further investigation into this revealed that this is because of
DCTCP's aggressive congestion window size reduction strategy on incast. The
proposed solution for incast problem is to use dynamic buffer allocation in
switches which is not implemented in our test setup. General performance of
DCTCP is not satisfactory either. For some experiments it even under performs
ECMP.  According to DCTCP paper it is optimized for some specific data center
traffic patterns like web search, soft real-time applications, recommendation
systems etc which we don't include in our experiments.

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=1\linewidth]{rate.png}
	\caption{Average bisection bandwidth}
	\label{fig:rate}
\end{figure*}

In Figure \ref{fig:rate} we show the aggregate bisection bandwidth. Iroko
consistently provides better utilization compared to ECMP and DCTCP in almost
all experiments. As expected non-blocking is providing the best performance out
of all four techniques. Utilization of non-blocking is lower for traffic
patterns with high incast. Hedera perform extremely well in all experiments
except for some like stride1, stag2$(0.5,0.3)$ where Iroko outperforms Hedera.
Interestingly enough, Hedera even outperforms non-blocking limit in stride8
experiment. ECMP does reasonably well when there is high probability of local
communication for example smaller strides, but start to deteriorate as the
stride length increases because of hash collisions.

Another interesting observation is that DCTCP gives abysmal utilization for some
experiments, for example randx2 and randx4. Further investigation into this
revealed that this is because of DCTCP's aggressive congestion window size
reduction strategy on incast. The proposed solution for incast problem is to use
dynamic buffer allocation in switches which is not implemented in our test
setup. General performance of DCTCP is not satisfactory either. For some
experiments it even under performs ECMP.  According to DCTCP paper it is
optimized for some specific data center traffic patterns like web search, soft
real-time applications, recommendation systems etc which we don't include in our
experiments.

\subsection{Drop rate}

\begin{figure*}
	\centering
	\includegraphics[width=1\linewidth]{qlen.png}
	\caption{CDF of queue lengths}
	\label{fig:qlen}
\end{figure*}

To analyze the drop rate we measured the number of packets built up in the queue
on all switches for the same set of traffic patterns and plotted a cumulative
distribution graph (Figure \ref{fig:qlen}). A high queue size is considered to
be bad. We have fixed the maximum queue size to 50 packets.

Iroko is not doing a good job here by consistently keeping $90\%$ of the queues
empty and rest $10\%$ full. But it is interesting to note that Iroko performs
really well for traffic patterns like stride1, stag2$(0.5,0.3)$ etc where it
shows high utilization as well. DCTCP maintains the queues to the minimum across
all experiments. This is not surprising considering the low utilization of
DCTCP. ECMP and Hedera behaves almost the same. Nonblocking has the highest
queue size out of all techniques. We believe that the CPU is the bottleneck here
since it only uses a single switch to connect the entire network.

Iroko definitely need more fine tuning for the prediction algorithm. We also
need to investigate why the graph has a sudden jump from $0$ to $50$. Initial
analysis shows that a small fixed set of switches are the bottleneck in all
experiments. Our guess is that this happens because of the unfair bandwidth
allocation across traffic flows. Analyzing fairness might provide better insight
into this problem.
